Complex Analysis of Askaryan Radiation: Towards UHE-$\nu$ energy Reconstruction via the Hilbert Envelope of Observed Signals

### 2025-02-13 template.tex
reached a milestone, but does it all make sense?  the final expression is there, now we have to check it

The function $G(z_0)$ is a function with odd-symmetry known as the Goodwin-Staton integral.  $G(z_0)$ appears in radiation transport, neutron transport, and optical calculations.  It is commonly used in problems involving diffusion approximations, particularly in media with semi-infinite boundary conditions. The final segment of the contour is
\begin{equation}
I_4 = \frac{j}{z_0}\int_{0}^{x} e^{x'^2} dx'
\end{equation}
The sum of contour segments is $I_1 + I_2 + I_3 + I_4 = I_{\rm C}$, where $I_{\rm C}$ is given by the Cauchy integral formula: $2\pi j e^{z_1^2}$.  Solving for $I(x,z_0)$, we find
\begin{equation}
I(x,z_0) = 2\pi j e^{z_1^2} - G(z_0) - \frac{j}{z_0}\int_{0}^{x} e^{x'^2} dx'
\end{equation}
If $x < \Im\lbrace z_0\rbrace$,
\begin{equation}
I(x,z_0) = -G(z_0) - \frac{j}{z_0}\int_{0}^{x} e^{x'^2} dx'
\end{equation} \\
Inserting this result into Eq. \ref{eq:withI},
\begin{multline}
r_a(t) * s_a(t) = \\ -\frac{j}{\sqrt{\pi}} R_0 E_0 \sigma_t^2 \left(\frac{dA(x,z_0)}{dx}-\frac{j}{z_0}\frac{dD(x)}{dx} \right) \label{eq:ra_sa_1}
\end{multline}
with
\begin{align}
A(x,z_0) &= 2\pi j e^{z_1^2} e^{-x^2} - G(z_0)e^{-x^2}, ~~ x > \Im \lbrace z_0 \rbrace\\
A(x,z_0) &= -G(z_0)e^{-x^2}, ~~ x < \Im \lbrace z_0 \rbrace
\end{align}
and
\begin{equation}
D(x) = e^{-x^2} \int_{0}^{x} e^{x'^2} dx'
\end{equation}
What remains is to compute the magnitude of Eq. \ref{eq:ra_sa_1}.  Let the overall scale factor in Eq. \ref{eq:ra_sa_1} be $R_0 E_0 \sigma_t^2/\sqrt{\pi}$, let $z_0 = x_0 + j y_0$, $\phi_0 = \tan^{-1}(y_0/x_0)$, and let $x>\Im\lbrace z_0\rbrace$.  Upon taking the magnitude, the quantity in parentheses generates four terms.  The first is
\begin{multline}
\left(\frac{dA}{dx}\right)^{*}\left(\frac{dA}{dx}\right) = \\ 16\pi^2|z_0|^2 e^{-4x y_0 - 2(x_0^2-y_0^2)} \\ + 4G^2(z_0)x^2 e^{-2x^2} \\ - 16\pi G(z_0) x e^{-x^2}e^{-2xy_0} e^{-x_0^2+y_0^2} \\ \times \left(|z_0|\cos(2x_0(x-y_0)+\phi_0) \right)
\end{multline}
The second is
\begin{equation}
\frac{1}{|z_0|^2}\left(\frac{dD(x)}{dx}\right)^2 = \frac{1}{|z_0|^2}\left(1-4xD(x)+4x^2D^2(x) \right)
\end{equation}
The combination of the third and forth terms is
\begin{multline}
j\frac{dD}{dx}\left\lbrace \frac{1}{z_0^{*}} \left(\frac{dA}{dx}\right) - \frac{1}{z_0} \left(\frac{dA}{dx}\right)^{*}\right\rbrace = \\
\end{multline}
\end{itemize}

>>>>

The function $G(z_0)$ is a function with odd-symmetry known as the Goodwin-Staton integral.  $G(z_0)$ appears in radiation transport, neutron transport, and optical calculations.  It is commonly used in problems involving diffusion approximations, particularly in media with semi-infinite boundary conditions. The final segment of the contour is
\begin{equation}
I_4 = \frac{j}{z_0}\int_{0}^{x} e^{x'^2} dx'
\end{equation}
The sum of contour segments is $I_1 + I_2 + I_3 + I_4 = I_{\rm C}$, where $I_{\rm C}$ is given by the Cauchy integral formula: $2\pi j e^{z_1^2}$.  Solving for $I(x,z_0)$, we find
\begin{equation}
I(x,z_0) = 2\pi j e^{z_1^2} - G(z_0) - \frac{j}{z_0}\int_{0}^{x} e^{x'^2} dx'
\end{equation}
If $x < \Im\lbrace z_0\rbrace$,
\begin{equation}
I(x,z_0) = -G(z_0) - \frac{j}{z_0}\int_{0}^{x} e^{x'^2} dx'
\end{equation} \\
Inserting this result into Eq. \ref{eq:withI},
\begin{multline}
r_a(t) * s_a(t) = \\ -\frac{j}{\sqrt{\pi}} R_0 E_0 \sigma_t^2 \left(\frac{dA(x,z_0)}{dx}-\frac{j}{z_0}\frac{dD(x)}{dx} \right) \label{eq:ra_sa_1}
\end{multline}
with
\begin{align}
A(x,z_0) &= 2\pi j e^{z_1^2} e^{-x^2} - G(z_0)e^{-x^2}, ~~ x > \Im \lbrace z_0 \rbrace\\
A(x,z_0) &= -G(z_0)e^{-x^2}, ~~ x < \Im \lbrace z_0 \rbrace
\end{align}
and
\begin{equation}
D(x) = e^{-x^2} \int_{0}^{x} e^{x'^2} dx'
\end{equation}
What remains is to compute the magnitude of Eq. \ref{eq:ra_sa_1}.  Let the overall scale factor in Eq. \ref{eq:ra_sa_1} be $R_0 E_0 \sigma_t^2/\sqrt{\pi}$, let $z_0 = x_0 + j y_0$, $\phi_0 = \tan^{-1}(y_0/x_0)$, and let $x>\Im\lbrace z_0\rbrace$.  Upon taking the magnitude, the quantity in parentheses generates four terms.  The first is
\begin{multline}
\left(\frac{dA}{dx}\right)^{*}\left(\frac{dA}{dx}\right) = \\ 16\pi^2|z_0|^2 e^{-4x y_0 - 2(x_0^2-y_0^2)} \\ + 4G^2(z_0)x^2 e^{-2x^2} \\ - 16\pi G(z_0) x e^{-x^2}e^{-2xy_0} e^{-x_0^2+y_0^2} \\ \times \left(|z_0|\cos(2x_0(x-y_0)+\phi_0) \right)
\end{multline}
The second is
\begin{equation}
\frac{1}{|z_0|^2}\left(\frac{dD(x)}{dx}\right)^2 = \frac{1}{|z_0|^2}\left(1-4xD(x)+4x^2D^2(x) \right)
\end{equation}
The combination of the third and fourth terms is
\begin{multline}
\frac{dD}{dx}\left\lbrace \frac{j}{z_0^{*}} \left(\frac{dA}{dx}\right) - \frac{j}{z_0} \left(\frac{dA}{dx}\right)^{*}\right\rbrace = \\
\frac{1}{|z_0|}\frac{dD}{dx}\left\lbrace e^{j\phi_0+j\pi/2} \left(\frac{dA}{dx}\right) + e^{-j\phi_0-j\pi/2} \left(\frac{dA}{dx}\right)^{*}\right\rbrace = \\ 
\frac{1}{|z_0|}\frac{dD}{dx}2\Re\left\lbrace e^{j\phi_0+j\pi/2} \left(\frac{dA}{dx}\right) \right\rbrace \label{eq:cross_terms}
\end{multline}
The expression in Eq. \ref{eq:cross_terms} simplifies to
\begin{multline}
\frac{1}{|z_0|}\frac{dD}{dx}2\Re\left\lbrace e^{j\phi_0+j\pi/2} \left(\frac{dA}{dx}\right) \right\rbrace = \\
(8\pi\sin(2x_0(x-y_0)+2\phi_0)e^{-2xy_0}e^{-x_0^2+y_0^2} \\ -2xG(z_0)\sin(\phi_0) e^{-x^2})\frac{dD}{dx}
\end{multline}
Finally, we add the results of the four terms generated, and take the square root:
\begin{multline}
\frac{1}{2}| x_a (t) * y_a(t)| = \\
16\pi^2|z_0|^2 e^{-4x y_0 - 2(x_0^2-y_0^2)} + \\ 4G^2(z_0)x^2 e^{-2x^2} - \\ 16\pi G(z_0) x e^{-x^2}e^{-2xy_0} e^{-x_0^2+y_0^2} \\ \times \left(|z_0|\cos(2x_0(x-y_0)+\phi_0) \right) + \\
\frac{1}{|z_0|^2}\left(1-4xD(x)+4x^2D^2(x) \right) + \\
\frac{dD}{dx}(8\pi\sin(2x_0(x-y_0)+2\phi_0)e^{-2xy_0}e^{-x_0^2+y_0^2} - \\ 2xG(z_0)\sin(\phi_0) e^{-x^2})
\end{multline}
\end{itemize}
